### 2022-03-28 README.Rmd
Actions.
add cran installation to readme

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![Build Status](https://travis-ci.com/zabore/ppseq.svg?branch=main)](https://travis-ci.com/zabore/ppseq) [![CRAN status](https://www.r-pkg.org/badges/version/ppseq)](https://CRAN.R-project.org/package=ppseq)
[![Codecov test coverage](https://codecov.io/gh/zabore/ppseq/branch/main/graph/badge.svg)](https://codecov.io/gh/zabore/ppseq?branch=main)
<!-- badges: end -->

The goal of ppseq is to provide functions that aid in designing clinical trials with sequential posterior probability monitoring incorporated.

@@

You can install the development version of ppseq from GitHub with:

>>>>

<!-- badges: start -->
[![R-CMD-check](https://github.com/zabore/ppseq/workflows/R-CMD-check/badge.svg)](https://github.com/zabore/ppseq/actions)
[![Codecov test coverage](https://codecov.io/gh/zabore/ppseq/branch/main/graph/badge.svg)](https://codecov.io/gh/zabore/ppseq?branch=main)
<!-- badges: end -->

The goal of ppseq is to provide functions to design clinical trials using sequential predictive probability monitoring for futility stopping.

@@

You can install the production version of ppseq from CRAN with:

```r
install.packages("ppseq")
```

Or you can install the development version of ppseq from GitHub with:
